Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Fix some typos

Bayesian Quadrature has its difficulties, however. While in our case
$S$ is a non-negative likelihood function, GP regression enforces no
such constraint. In an effort to avoid this problem,
\cite{Osborne:2012tm} give a method which involves instead placing a
prior over the log liklihood\footnote{In practice, as in
  \cite{Osborne:2012tm}, we use the transform of $\log(S+1)$.}, thus
ensuring that $S=e^{\log S}$ will be positive\footnote{We are not
  guaranteed positivity, however, the approximation to the integral
  over $\log S$ (Equation \ref{eq:bq-Z-mean}) requires computing
  $\mu_S$, which may have nonpositive segments.}:
\begin{equation*}
  E[Z\ \vert \ \log S]=\int_{\log S}\left(\int_R \exp(\log{S(X_b,X_R)})p(R)\ \mathrm{d}R\right)\mathcal{N}\left(\log{S}\ \vert \ \mu_{\log S}, \Sigma_{\log S}\right)\ \mathrm{d}\log S
\end{equation*}
where $\mu_{\log S}$ and $\Sigma_{\log S}$ are the mean and
covariance, respectively, of the GP regression over $\log S$ given
$\mathbf{R}$. We approximate this according to the method given in
\cite{Osborne:2012tm}:
\begin{equation}
  \mu_Z=E[Z\ \vert \ S, \log S, \Delta_c] \approx \int_R \mu_{S}(1 + \mu_\Delta) p(R)\ \mathrm{d}R 
  \label{eq:bq-Z-mean}
\end{equation}
where $\mu_S$ is the mean of a GP regression over $S$ given
$\mathbf{R}$; and $\mu_{\Delta_c}$ is a regression over
$\Delta_c=\mu_{\log S} - \log \mu_S$ given $\mathbf{R}_c$, which
consists of $\mathbf{R}$ and a set of intermediate \emph{candidate
  points}\footnote{These candidate points do not require evaluating
  the true $S$, only the GP estimates of $S$ and $\log S$.} $c$ as
described in \cite{Osborne:2012tm}. The variance of the estimate of
$Z$ is given by:
\begin{equation}
  \sigma_Z=\mathrm{Var}(Z\ \vert \ S, \log S, \Delta_c) = \int_R\int_{R^\prime} \mu_S(R)\mu_S(R^\prime) \Sigma_{\log S}(R, R^\prime)p(R)p(R^\prime)\ \mathrm{d}R\ \mathrm{d}R^\prime
  \label{eq:bq-Z-var}
\end{equation}

@@

Like the na\"ive model, the parametric model uses hill-climbing as a
sampling strategy, so they have identical correlations with the true
angle of rotation. However, given the same $\mathbf{R}$, the
parametric model estimates $Z$ differently, thus giving rise to
different response and estimated $Z$ error rates. The response error
for the parametric model was higher than the na\"ive model, with
$\mathrm{ME}=0.26$. Breaking this down, we see that the error for
$h_1$ stimuli is $\mathrm{ME}=0.5$: in other words, the parametric
model is at chance when determining whether two identical shapes are
the same. This is because it never overestimates (see Figure
\ref{fig:accuracy}, center panel). So, it accurately estimates $Z$ for
stimuli which the na\"ive model would overestimate
($\mathrm{MSE}=0.07$), but still has poor performance when $Z$ is
underestimated. Indeed, if we exclude stimuli for which the nai\"ive
model overestimates ($Z\geq 3$), the error for the na\"ive model
lowers to match that of the parametric model.

>>>>

Bayesian Quadrature has its difficulties, however. While in our case
$S$ is a non-negative likelihood function, GP regression enforces no
such constraint. In an effort to avoid this problem,
\cite{Osborne:2012tm} give a method which involves instead placing a
prior over the log liklihood\footnote{In practice, as in
  \cite{Osborne:2012tm}, we use the transform of $\log(S+1)$.}, thus
ensuring that $S=e^{\log S}$ will be positive\footnote{We are not
  guaranteed positivity, however, the approximation to the integral
  over $\log S$ (Equation \ref{eq:bq-Z-mean}) requires computing
  $\mu_S$, which may have nonpositive segments.}:
\begin{equation*}
  E[Z\ \vert \ \log S]=\int_{\log S}\left(\int_R \exp(\log{S(X_b,X_R)})p(R)\ \mathrm{d}R\right)\mathcal{N}\left(\log{S}\ \vert \ \mu_{\log S}, \Sigma_{\log S}\right)\ \mathrm{d}\log S
\end{equation*}
where $\mu_{\log S}$ and $\Sigma_{\log S}$ are the mean and
covariance, respectively, of the GP regression over $\log S$ given
$\mathbf{R}$. We approximate this according to the method given in
\cite{Osborne:2012tm}:
\begin{equation}
  \mu_Z=E[Z\ \vert \ S, \log S, \Delta_c] \approx \int_R \mu_{S}(1 + \mu_{\Delta_c}) p(R)\ \mathrm{d}R 
  \label{eq:bq-Z-mean}
\end{equation}
where $\mu_S$ is the mean of a GP regression over $S$ given
$\mathbf{R}$; and $\mu_{\Delta_c}$ is a regression over
$\Delta_c=\mu_{\log S} - \log \mu_S$ given $\mathbf{R}_c$, which
consists of $\mathbf{R}$ and a set of intermediate \emph{candidate
  points}\footnote{These candidate points do not require evaluating
  the true $S$, only the GP estimates of $S$ and $\log S$.} $c$ as
described in \cite{Osborne:2012tm}. The variance of the estimate of
$Z$ is given by:
\begin{equation}
  \sigma_Z=\mathrm{Var}(Z\ \vert \ S, \log S, \Delta_c) = \int_R\int_{R^\prime} \mu_S(R)\mu_S(R^\prime) \Sigma_{\log S}(R, R^\prime)p(R)p(R^\prime)\ \mathrm{d}R\ \mathrm{d}R^\prime
  \label{eq:bq-Z-var}
\end{equation}

@@

Like the na\"ive model, the parametric model uses hill-climbing as a
sampling strategy, so they have identical correlations with the true
angle of rotation. However, given the same $\mathbf{R}$, the
parametric model estimates $Z$ differently, thus giving rise to
different response and estimated $Z$ error rates. The response error
for the parametric model was higher than the na\"ive model, with
$\mathrm{ME}=0.26$. Breaking this down, we see that the error for
$h_1$ stimuli is $\mathrm{ME}=0.5$: in other words, the parametric
model is at chance when determining whether two identical shapes are
the same. This is because it never overestimates (see Figure
\ref{fig:accuracy}, center panel). So, it accurately estimates $Z$ for
stimuli which the na\"ive model would overestimate
($\mathrm{MSE}=0.07$), but still has poor performance when $Z$ is
underestimated. Indeed, if we exclude stimuli for which the na\"ive
model overestimates ($Z\geq 3$), the error for the na\"ive model
lowers to match that of the parametric model.
